Modeling Time-Variable Elemental Abundances in Coronal Loop Simulations

### 2024-05-08 src/tex/ms.tex
[showyourwork] overleaf sync

\acknowledgments  
At the time of writing, the implementation into \texttt{ebtel++} is publicly available as an unmerged pull request on GitHub: \url{https://github.com/rice-solar-physics/ebtelPlusPlus/pull/87}.

>>>>

\begin{acknowledgements}
At the time of writing, the implementation into \texttt{ebtel++} is publicly available as an unmerged pull request on GitHub: \url{https://github.com/rice-solar-physics/ebtelPlusPlus/pull/87}.
\end{acknowledgements}
